Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and attentional function: A study based on the parametric g-formula

### 2024-04-10 output/paper/manuscript.qmd
Trying to convert md to docx manually.

embed-resources: true
format:
  docx:
    page-width: 8.3
    citeproc: true
    mermaid:
      theme: neutral
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
    pdf-engine: lualatex
    number-sections: true
    toc: false
    keep-tex: false
    include-in-header:
      text: |
        \usepackage{lineno}
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
    include-before-body:
      text: |
        \linenumbers

>>>>

embed-resources: true
format:
  docx:
    page-width: 8.3
    citeproc: true
    mermaid:
      theme: neutral
    keep-md: true
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
    pdf-engine: lualatex
    number-sections: true
    toc: false
    keep-tex: false
    include-in-header:
      text: |
        \usepackage{lineno}
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
    include-before-body:
      text: |
        \linenumbers
